### 2009-02-23 pkg/vcd/paper/Shadings/JCGS.Rnw
rearrange repository
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@690 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\pagestyle{fancy}
\thispagestyle{fancyplain}
\headrulewidth0pt
\lhead[]{}
\chead[]{}
\rhead[]{}
\lfoot[This is a preprint of an article accepted for publication in \textit{Journal of Computational and Graphical Statistics}.
Copyright {\copyright} 2007 American Statistical Association, Institute of Mathematical Statistics, and Interface Foundation of North America]%
{This is a preprint of an article accepted for publication in \textit{Journal of Computational and Graphical Statistics}.
Copyright {\copyright} 2007 American Statistical Association, Institute of Mathematical Statistics, and Interface Foundation of North America}
\cfoot[]{}
\rfoot[]{}

@@

The results in this paper were obtained using
\proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")}
\citep[\mbox{\url{http://www.R-project.org/}}]{vcd:R:2006} and the packages
\pkg{vcd}~\Sexpr{packageDescription("vcd")$Version} \citep{vcd:Meyer+Zeileis+Hornik:2006b},
{\pkg{MASS}~\Sexpr{packageDescription("MASS")$Version}} \citep[see][]{vcd:Venables+Ripley:2002},
{\pkg{grid}~{\Sexpr{packageDescription("grid")$Version}}} \citep[see][]{vcd:Murrell:2002} and
{\pkg{colorspace}~{\Sexpr{packageDescription("colorspace")$Version}}} \citep{vcd:Ihaka:2004}.
A vignette that demonstrates how all empirical examples can exactly be reproduced
in \proglang{R} is provided in the package \pkg{vcd}, see
\code{vignette("residual-shadings", package = "vcd")}.

>>>>

\pagestyle{fancy}
\thispagestyle{fancyplain}
\headrulewidth0pt
\lhead[]{}
\chead[]{}
\rhead[]{}
\lfoot[This is a preprint of an article published in \textit{Journal of Computational and Graphical Statistics}, Volume 16, Number 3, Pages 507--525.
Copyright {\copyright} 2007 American Statistical Association, Institute of Mathematical Statistics, and Interface Foundation of North America]%
{This is a preprint of an article published in \textit{Journal of Computational and Graphical Statistics}, Volume 16, Number 3, Pages 507--525.
Copyright {\copyright} 2007 American Statistical Association, Institute of Mathematical Statistics, and Interface Foundation of North America}
\cfoot[]{}
\rfoot[]{}

@@

The results in this paper were obtained using
\proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")}
\citep[\mbox{\url{http://www.R-project.org/}}]{vcd:R:2006} and the packages
\pkg{vcd}~\Sexpr{packageDescription("vcd")$Version} \citep{vcd:Meyer+Zeileis+Hornik:2006b},
{\pkg{MASS}~\Sexpr{packageDescription("MASS")$Version}} \citep[see][]{vcd:Venables+Ripley:2002},
{\pkg{grid}~{\Sexpr{packageDescription("grid")$Version}}} \citep[see][]{vcd:Murrell:2002} and
{\pkg{colorspace}~{\Sexpr{packageDescription("colorspace")$Version}}} \citep{vcd:Ihaka:2006}.
A vignette that demonstrates how all empirical examples can exactly be reproduced
in \proglang{R} is provided in the package \pkg{vcd}, see
\code{vignette("residual-shadings", package = "vcd")}.
